%% ============================================================
%%  JAYESH CHAUDHARI — DATA ENGINEER RESUME
%%  Top 5% | ATS-Optimised | 6-Second Scan Ready
%% ============================================================

\documentclass[10pt, a4paper]{article}

\usepackage[a4paper, top=0.45in, bottom=0.45in, left=0.55in, right=0.55in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{tabularx}
\usepackage{array}
\usepackage{fontawesome5}
\usepackage{parskip}

%% ── Colours ─────────────────────────────────────────────────
\definecolor{accent}{HTML}{1A56DB}
\definecolor{darkgray}{HTML}{1F2937}
\definecolor{midgray}{HTML}{4B5563}
\definecolor{lightgray}{HTML}{6B7280}
\definecolor{rulecol}{HTML}{DBEAFE}

\hypersetup{colorlinks=true, urlcolor=accent, linkcolor=accent, pdfborder={0 0 0}}
\pagestyle{empty}

%% ── Section formatting ──────────────────────────────────────
\titleformat{\section}
    {\large\bfseries\color{darkgray}}{}{0em}{}
    [\vspace{-4pt}\textcolor{accent}{\rule{\linewidth}{1.2pt}}\vspace{2pt}]
\titlespacing{\section}{0pt}{7pt}{3pt}

%% ── List formatting ─────────────────────────────────────────
\setlist[itemize]{
    leftmargin=1.2em, itemsep=0.5pt,
    parsep=0pt, topsep=1pt,
    label=\textcolor{accent}{\small\textbullet}
}

%% ── Custom commands ─────────────────────────────────────────
\newcommand{\jobentry}[4]{%
    \noindent
    \begin{tabularx}{\linewidth}{@{}X r@{}}
        {\bfseries\color{darkgray} #1} \textcolor{lightgray}{|}
        \textcolor{accent}{#2} & \textcolor{lightgray}{\small #3} \\
        \textcolor{midgray}{\small\itshape #4} & \\
    \end{tabularx}\vspace{2pt}
}

\newcommand{\projectentry}[3]{%
    \noindent
    \begin{tabularx}{\linewidth}{@{}X r@{}}
        {\bfseries\color{darkgray} #1}
        \textcolor{lightgray}{\small | \textit{#2}}
        & \textcolor{accent}{\small\faGithub\
          \href{#3}{github.com/jayeshchaudha}} \\
    \end{tabularx}\vspace{2pt}
}

\newcommand{\certentry}[3]{%
    \noindent{\bfseries\color{darkgray} #1}
    \textcolor{lightgray}{|} \textcolor{midgray}{\small #2}
    \hfill \textcolor{lightgray}{\small #3}\\[-2pt]
}

\newcommand{\skillrow}[2]{%
    \noindent{\bfseries\color{darkgray}\small #1:}
    \textcolor{midgray}{\small #2}\\[2pt]
}

%% ============================================================
\begin{document}

%% ── HEADER ──────────────────────────────────────────────────
\begin{center}
    {\Huge\bfseries\color{darkgray} Jayesh Chaudhari}\\[4pt]
    {\large\color{accent}\bfseries Data Engineer}\\[6pt]
    \textcolor{midgray}{\small
        \faMapMarker*\ Pune, Maharashtra \quad
        \faPhone\ +91-94052-76764 \quad
        \faEnvelope\ \href{mailto:chaudharij1503@gmail.com}{chaudharij1503@gmail.com}
    }\\[3pt]
    \textcolor{midgray}{\small
        \faLinkedin\ \href{https://linkedin.com/in/jchau1503}{linkedin.com/in/jchau1503} \quad
        \faGithub\ \href{https://github.com/jayeshchaudha}{github.com/jayeshchaudha} \quad
        \faGlobe\ \href{https://jayeshchaudha.github.io}{jayeshchaudha.github.io}
    }
\end{center}

\vspace{2pt}
\noindent\textcolor{rulecol}{\rule{\linewidth}{0.8pt}}
\vspace{2pt}

%% ── PROFESSIONAL SUMMARY ─────────────────────────────────────
\section{Professional Summary}

\textcolor{midgray}{
Data Engineer with \textbf{4+ years} of experience in data pipelines, analytics engineering,
and business intelligence across \textbf{energy, manufacturing, and retail domains}.
Electrical Engineering background combined with enterprise-level data work at
\textbf{Enbridge (Fortune 500, Canada)} gives rare domain depth --- uniquely positioned
for \textbf{industrial IoT, energy analytics, and cloud pipeline} roles.
Proven delivery: \textbf{98\%+ data accuracy} on 100+ monthly validations, \textbf{40\%}
reduction in manual reporting effort, and end-to-end SQL and Python pipeline development.
Certified in \textbf{Azure (DP-203)} and \textbf{Databricks}; experienced with
PySpark, Airflow, Snowflake, and DBT.
}

%% ── TECHNICAL SKILLS ─────────────────────────────────────────
\section{Technical Skills}

\skillrow{Languages}{Python (Pandas, NumPy, openpyxl), SQL (Advanced), VBA (Intermediate), Bash (Basic)}
\skillrow{Data Engineering}{Apache Airflow, PySpark, DBT Core, ETL pipeline design, incremental loads, data modelling}
\skillrow{Cloud --- Azure}{Azure Data Factory, Azure Data Lake Storage Gen2, Azure Synapse Analytics, Azure Databricks}
\skillrow{Warehousing}{Snowflake, Delta Lake, PostgreSQL, MySQL, star schema / SCD design}
\skillrow{Streaming}{Apache Kafka (producers/consumers), Azure Event Hubs (awareness)}
\skillrow{Data Quality}{Great Expectations, schema validation, data reconciliation, audit trail design}
\skillrow{BI \& Reporting}{Power BI (DAX, data modelling), Excel (Advanced --- pivot tables, Power Query, VBA)}
\skillrow{DevOps}{Git, GitHub Actions, Docker (basic), Terraform (basic)}
\skillrow{Domain}{Energy DSM data, electrical systems QC, manufacturing KPIs (OEE), IoT sensor data}
\skillrow{Enterprise}{SAP, CRM platforms, A/P batch processing, vendor data management}

%% ── WORK EXPERIENCE ──────────────────────────────────────────
\section{Work Experience}

%% -- Job 1 --
\jobentry{DSM Tracking \& Reporting Analyst}{Enbridge Inc.}%
    {Jan 2024 -- Feb 2026}{Toronto, Canada \ \textbar\ Energy Sector \textbar\ Fortune 500 \textbar\ Remote}

\begin{itemize}
    \item Designed and maintained \textbf{data validation pipelines} for 100+ monthly DSM projects
    and customer incentive payments --- achieved \textbf{98\%+ accuracy} across all submissions.
    \item Built \textbf{Excel/VBA automated dashboards} for senior management, cutting report
    generation time by \textbf{35\%} and eliminating 8+ hours of manual weekly effort.
    \item Processed and reconciled \textbf{CRM and A/P batch data} for 50+ vendors monthly ---
    validated equipment eligibility across \textbf{200+ annual projects} with 100\% audit compliance.
    \item Resolved \textbf{50+ monthly data discrepancies} between CRM platforms and financial
    systems, reducing DNQ (Did Not Qualify) claims and protecting shareholder payouts.
    \item Engineered data quality rules and lookup validation logic to catch payment errors
    pre-submission --- reduced rework rate by an estimated \textbf{25\%}.
\end{itemize}

\vspace{3pt}

%% -- Job 2 --
\jobentry{Junior Data Analyst}{NPower Canada}{May 2023 -- Aug 2023}%
    {Toronto, Canada \textbar\ Data Analytics Program}

\begin{itemize}
    \item Built \textbf{automated SQL reporting pipelines} reducing manual reporting time by
    \textbf{40\%}; performed statistical analysis and EDA on real-world datasets.
    \item Delivered findings and business recommendations to stakeholders --- practised
    translating raw data into decisions, a skill applied directly in pipeline design.
\end{itemize}

\vspace{3pt}

%% -- Job 3 --
\jobentry{Quality Engineer}{Mass-Tech Controls Pvt. Ltd.}{2018 -- 2019}%
    {Jalgaon, Maharashtra \textbar\ Electrical Systems Manufacturing}

\begin{itemize}
    \item Tested and analysed \textbf{DC systems, rectifiers, switchgear, and inverters} against
    quality standards --- maintained \textbf{100\% QC compliance} documentation.
    \item Conducted root cause analysis on equipment failures --- built systematic debugging
    mindset now applied to pipeline failures and data quality investigations.
\end{itemize}

%% ── PROJECTS ─────────────────────────────────────────────────
\section{Projects}

%% -- Project 1 --
\projectentry{Energy DSM Pipeline --- Azure End-to-End DE Project}%
    {Python $\cdot$ Azure Data Factory $\cdot$ ADLS Gen2 $\cdot$ Snowflake $\cdot$ Airflow}%
    {https://github.com/jayeshchaudha/energy-dsm-pipeline}

\begin{itemize}
    \item Built a cloud pipeline simulating Enbridge-style DSM project data flows:
    raw CSV ingestion $\rightarrow$ Azure Data Lake Gen2 $\rightarrow$ Python transformation
    (PySpark) $\rightarrow$ Snowflake $\rightarrow$ Power BI --- processing \textbf{500K+
    records} per run.
    \item Implemented \textbf{Great Expectations} data quality checks (null validation, value
    range checks, schema enforcement) with \textbf{Airflow DAG} orchestration and email
    alerts on failure.
    \item Applied real domain knowledge from Enbridge --- DSM eligibility rules, vendor
    lookup validation, and audit trail logging built directly into the pipeline.
\end{itemize}

\vspace{2pt}

%% -- Project 2 --
\projectentry{E-Commerce SQL Analytics --- Business Intelligence Pipeline}%
    {SQL $\cdot$ Python $\cdot$ PostgreSQL $\cdot$ Power BI}%
    {https://github.com/jayeshchaudha/E-commerce-SQL-Analysis}

\begin{itemize}
    \item Designed \textbf{5 business-driven SQL analyses} on UCI Online Retail Dataset
    (500K+ transactions): revenue trends, customer lifetime value, \textbf{RFM segmentation},
    cancellation analysis, and geographic distribution.
    \item Structured queries as modular, reusable CTEs --- mirroring a \textbf{DBT project
    layout} with staging, intermediate, and mart layers; loaded results into PostgreSQL and
    visualised in Power BI.
    \item Documented business questions, query logic, and findings structured for
    stakeholder presentation.
\end{itemize}

\vspace{2pt}

%% -- Project 3 --
\projectentry{DBT + Snowflake Analytics Engineering Project}%
    {DBT $\cdot$ Snowflake $\cdot$ Python $\cdot$ Airflow $\cdot$ Great Expectations}%
    {https://github.com/jayeshchaudha/dbt-snowflake-analytics}

\begin{itemize}
    \item Built a complete \textbf{DBT project} on Snowflake transforming raw retail event
    data into a star schema --- fact tables, dimension tables, business metrics, and
    automated data tests.
    \item Orchestrated DBT runs via \textbf{Airflow DAG} with Great Expectations pre-checks
    and Slack failure alerts; published full \textbf{data lineage} via DBT docs on GitHub Pages.
    \item Implemented \textbf{SCD Type 2} for customer dimension --- tracks historical changes
    without data loss.
\end{itemize}

%% ── CERTIFICATIONS ───────────────────────────────────────────
\section{Certifications}

\certentry{Microsoft Azure Data Engineer Associate (DP-203)}{Microsoft}{2025}
\certentry{Databricks Certified Data Engineer Associate}{Databricks}{2025}
\certentry{Snowflake SnowPro Core Certification}{Snowflake}{2025}
\certentry{Microsoft Azure Fundamentals (AZ-900)}{Microsoft}{Jul 2023}
\certentry{IBM Data Analyst Professional Certificate}{IBM / Coursera}{Aug 2023}

%% ── EDUCATION ────────────────────────────────────────────────
\section{Education}

\noindent
\begin{tabularx}{\linewidth}{@{}X r@{}}
    {\bfseries\color{darkgray} Graduate Certificate, Project Management} \textcolor{lightgray}{|}
    \textcolor{accent}{Algonquin College, Ottawa, Canada}
    & \textcolor{lightgray}{\small Sep 2021 -- May 2022} \\
\end{tabularx}
\begin{tabularx}{\linewidth}{@{}X r@{}}
    {\bfseries\color{darkgray} Graduate Certificate, Energy Management} \textcolor{lightgray}{|}
    \textcolor{accent}{Algonquin College, Ottawa, Canada}
    & \textcolor{lightgray}{\small Jan -- Sep 2021} \\
\end{tabularx}
\begin{tabularx}{\linewidth}{@{}X r@{}}
    {\bfseries\color{darkgray} B.E., Electrical Engineering} \textcolor{lightgray}{|}
    \textcolor{accent}{Amravati University, Maharashtra}
    & \textcolor{lightgray}{\small 2013 -- 2017} \\
    \textcolor{midgray}{\small Relevant: Signals \& Systems, Control Systems,
    Electrical Machines, C Programming}
    & \\
\end{tabularx}

%% ── ACHIEVEMENTS ─────────────────────────────────────────────
\section{Achievements \& Activities}

\begin{itemize}
    \item \textbf{Technical Writing:} Published articles on Medium covering Azure pipeline
    design, Airflow DAG patterns, and energy data engineering --- targeted at the
    DE community.
    \item \textbf{Open Source:} Active GitHub contributor --- all projects include full
    README, architecture diagrams, and sample datasets for reproducibility.
    \item \textbf{Community:} Active member, Pune Data Engineering and Analytics meetup
    group --- regularly attends sessions on cloud DE and MLOps.
    \item \textbf{Domain Edge:} Only candidate profile combining Fortune 500 energy sector
    experience (Enbridge) + Electrical Engineering + cloud DE certifications in the
    Pune job market.
\end{itemize}

%% ── FOOTER ───────────────────────────────────────────────────
\vspace{4pt}
\noindent{\bfseries\color{darkgray}\small Languages:}
\textcolor{midgray}{\small English (Fluent), Hindi (Native), Marathi (Native)}
\hfill
{\bfseries\color{darkgray}\small Open to:}
\textcolor{midgray}{\small Pune \textbar\ Remote \textbar\ Hybrid}

\end{document}